\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{fontawesome}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[margin=0.5in]{geometry}
\usepackage{inter}

% Inter font
\usepackage{fontspec}
\setmainfont{Inter}

\pagestyle{plain}
\pagenumbering{gobble}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\definecolor{light}{gray}{0.2}
\definecolor{lighter}{gray}{0.4}
\definecolor{lightest}{gray}{0.6}
\definecolor{faint}{gray}{0.8}

%----------COMMANDS------------------
% Sections formatting
\titleformat{\section}{
  \vspace{8pt}\color{lighter}\interextrabold\raggedright\Large
}{}{0em}{}[\color{faint}\titlerule]

\newcommand{\resumeHeading}[3]{
  % \item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \\
    \color{lighter}\interlight\textit{\small#2} & \color{lighter}\interlight\textit{\small#3} \\
  \end{tabular*}
}

\newcommand{\tabularStart}{
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
  }

  \newcommand{\tabularEnd}{
  \end{tabular*}
}

\newcommand{\educationHeading}[2]{
  \intersemibold{#1} & {\small#2} \\
}

\newcommand{\educationItem}[2]{
  \color{lighter}\interlight\textit{\small#1} & \color{lighter}\interlight\textit{\small#2} \\
}

\newcommand{\resumeSubheading}[4]{
  
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \intersemibold{#1} & {\small#2} \\
    \color{lighter}\interlight\textit{\small#3} & \color{lighter}\interlight\textit{\small#4} \\
  \end{tabular*}
}

\newcommand{\resumeSubSubheading}[3]{
  \vspace{16pt}
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \intersemibold{#1} & \\
    \color{lighter}\interlight{\small#3} & \color{lighter}\interlight\textit{\small #2}\\
  \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}
\newcommand{\resumeItemListStart}{
\begin{itemize}[leftmargin=20pt]}
    \newcommand{\resumeItemListEnd}{
\end{itemize}}

%------------------------------------
\begin{document}

%----------HEADING-------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \interextrabold\Huge Adam Pearce\vspace{16pt} & \\

  \color{faint}\small\faEnvelope\normalsize\hspace{4pt}\color{light}\href{mailto:adamp319@gmail.com}{adamp319@gmail.com}
  & \color{faint}\large\faGithub\normalsize\hspace{4pt}\color{light}\href{https://github.com/adamhp}{github.com/adamhp} \\

  \color{faint}\faPhone\hspace{4pt}\color{light}\href{tel:+17573740780}{+1-757-374-0780}
  & \color{faint}\faLinkedin\hspace{4pt}\color{light}\href{https://www.linkedin.com/in/adamhp/}{linkedin.com/in/adamhp} \\

  & \color{faint}\small\faGlobe\normalsize\hspace{4pt}\color{light}\href{https://adamhp.io}{adamhp.io} \\

\end{tabular*}

\vspace{16pt}

Creative software engineer with product and design sense that has spent 10 years turning complex, high-stakes cybersecurity and defense challenges into intuitive, impactful products.

\vspace{8pt}

{\color{lighter}\intersemibold Tech}{: \color{light}Python, Flask, Django, React, TypeScript, NextJS, TailwindCSS, HTML/CSS, Postgres, NoSQL, Java, Spring, Docker, Kubernetes, OpenShift, Spark, AWS, git } \\
\color{black}

%-----------EDUCATION-----------------
\section{Education}
\tabularStart
\educationHeading{University of Virginia}{Charlottesville, VA}
\educationItem{M.S. Data Science}{2015}
\educationItem{B.A. Statistics (Econometrics)}{2014}
\tabularEnd

%-----------EXPERIENCE-----------------
\section{Experience}

\resumeHeading{Agile Defense}{Staff Software Engineer, Solutions Architect}{June 2015 -- Present}
\vspace{8pt}
\resumeSubSubheading{Solutions Architect}{March 2022 -- Present}{CISA, Integrated Operations Division}
\resumeItemListStart
\item Launched an agency-wide Common Operating Picture: a real-time geospatial platform aggregating tens of thousands of critical-infrastructure incidents; provided net-new capability for agency-wide situational awareness; briefed to members of Congress.
\item Built a zero-net-new-cost deployment-tracking system on M365/Power Platform covering thousands of personnel; became a standing brief to the Deputy Director; improved resourcing decisions and reduced coordination time.
\item Automated high-volume, high-criticality reports and workflows, improving consistency and quality while reducing delivery time by at least 50\%+ and returning $\sim$25-50 analyst hours/week to higher-value work.
\resumeItemListEnd

\resumeSubSubheading{Senior Software Engineer, Project Lead}{June 2018 -- March 2022}{Department of the Navy \& CISA}
\resumeItemListStart
\item Led 5 engineers to deliver a Python/React/Grafana/Timescale platform for Navy test analysis; replaced printed logs with a searchable, time-synced view of multivariate telemetry, geospatial data, video, and audio --- cutting analysis cycles from days to hours.
\item Directed a 10-engineer SRE/ops team for a 60-node OpenShift/Spark/Elasticsearch/Hadoop stack processing 300 GB--1 TB/day; improved reliability of legacy hardware system to 95\% uptime, reduced MTTR by 50\% via infrastructure automation, and significantly improved POAM and compliance posture.
\resumeItemListEnd

\resumeSubSubheading{Software Engineer, Technical Lead}{June 2015 -- June 2018}{CISA, Automated Indicator Sharing Platform}
\resumeItemListStart
\item Led product development for a 10-engineer team across 12+ production apps; delivered a variety of net-new capabilities to improve the cybersecurity and resilience of the United States.
\item Built core services (Java/Spring Cloud, Python/Flask, React) for a distributed platform sharing millions of cyber-threat indicators across hundreds of government and private partners; net-new capability serving as DHS's flagship cybersecurity sharing platform.
\item Drove migration to microservices on Spring Cloud + AWS + Kubernetes; designed NiFi-based ETL with fine-grained access controls and policy-driven dissemination; resulted in increased customer adoption due to improved performance and reliability of MSA.
\item Implemented CI/CD with Jenkins (build/test/security scans/phase-gated deploys), cutting time-to-production from 90 days to 10, significantly reducing production outages and standardizing releases across environments.
\resumeItemListEnd

\vspace{16pt}
\resumeHeading
{Pearce Labs, LLC.}
{Owner, Operator}{July 2025 -- Present}
\resumeItemListStart
\item Own and operate a digital services agency (\href{https://pearcelabs.com}{pearcelabs.com}), providing design, development, and business automation services for local small businesses
\resumeItemListEnd

%-----------PROJECTS-----------------
\section{Projects \& Interests}
\begin{itemize}[leftmargin=0pt]
  \item[]{\faLink\space \href{https://multiborder.io}{\intersemibold{https://multiborder.io}}}: An iOS app that creates borders around multiple images in different aspect ratios, in order to maximize viewability for social media without cropping. \\
  \item[]{\faLink\space \href{https://oeno.chat}{\intersemibold{https://oeno.chat}}}: GPT-powered wine recommendations that helps users find the perfect wine for any meal. \\
  \item[]{\intersemibold{Wildfire}}: Co-founded a SaaS product in the creator economy; startup failure \#1. Analyzed creators' Twitter audiences to discover unique customer profiles to derive opportunities for monetization. \\
  \item[]{\intersemibold{Lasso}}: Pivoted Wildfire to serve creators directly; startup failure \#2. A two-sided marketplace for creator discovery, brand campaigns, and brand-creator relationship management, including customized media kits for creators that showcased their audience and engagement metrics to help land better brand deals. \\
  \item[]{\intersemibold{Hobbies}}{}: Guitar, music composition, cooking, photography, design, tabletop RPGs, videogames, hiking, fly fishing, reading science fiction and fantasy, writing, microelectronics, gardening
\end{itemize}

\end{document}
